### 2014-08-30 fundamentals/qa.tex
more has been written

>>>>

\subsection{Documentation}

All of the public interface (the API) must be documented as part of cyclus
QA policy. This certifies that the intention for a code unit is communicated 
in way that is separate from its implementation. This policy is important 
because implementations are often wrong, hence bugs. They are thus unreliable 
resources about themselves. Truly trustworthy communication about what 
software should be doing comes from the author explicitly stating the 
goals of an API in prose form. Furure development of the code is then able to 
compare the implemetation versus the documentation to discern whether or not they 
are in agreement. Documentation is thus a secondary higher-level information 
stream.  In cyclus, this information is aggregated together into static 
websites with the doxygen \cite{van2008doxygen} and sphinx \cite{brandl2014sphinx} 
tools. These websites are placed online at \url{http://fuelcycle.org}.

\subsection{Version Control}

Version control is the history-preserving mechanism by which the provenance of 
a code is recored. Cyclus uses a well-established tool called git \cite{git_2014}
for this purpose. Git is currently the most popular utilty in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every 
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
Though there and many praises and criticisms of git, one 
feature that the tool performs exceptionally well is the notion of code branches.
These are distinct pathways in the history that branch out of a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
branches may exist at all point in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an 
accompanying message. Thus 
it is possible for cyclus to accurarely replay the entirety of who did what to the
code when.

Cyclus uses a strategy known as \emph{git flow} \cite{kalliamvakou2014code} 
to manage topical branches where individuals develop code, the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineation, cyclus also imposes rules on 
when it is accecptable from a quality control standpoint to merge code from 
the personal topical branches into develop. All software at this stage 
must have sufficient and passing tests and reasonable documentation. Without
these core pieces proposed changes are not allowed into cyclus.

The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
hosted remotely on the GitHub website \cite{dabbish2012social}. The online
mechanism for pull requests allows for code review by a member of the cyclus 
core team other than the author prior to any change being included. Non-members
of the cyclus development team are allowed and encouraged to submit and review 
pull requests. However, only members of the cyclus core team are allowed to 
merge in any changes and only after the QA standards have been met.

\subsection{Style Guide}

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this
coding style guides are the software analogy to the natural language ones, 
such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger2008google} for all software contributions.
